The importance of transient resonances in extreme-mass-ratio inspirals

### 2016-08-15 res_char.tex
Relaitve flux

%The absolute size of the resonance jump is often not particularly useful, especially when comparing different systems. Instead, we can express the resonance jump as a fraction of the adiabatic change expected across the resonance. For the orbital parameter $\mathcal{I}$,
%\begin{equation}
%\label{eq:res-jump-ratio}
%\frac{\Delta \mathcal{I}\sub{jump}}{\mathcal{I}\sub{ad}(t>t\sub{res})-\mathcal{I}\sub{ad}(t<t\sub{res})} = \frac{\Delta \mathcal{I}\sub{jump}}{\dot{\mathcal{I}}\sub{ad}(t\sub{res})\tau\sub{res}}.
%\end{equation}

@@

\begin{figure}
\centering
%\includegraphics[width=0.46\textwidth]{res_flux_rms_p}
\includegraphics[width=0.46\textwidth]{Fig_e_rms_p}
\caption{\label{fig:res-flux-rms-p}Relative flux enhancements of $p$, as a function of $e$, marginalised over $a_\ast$ and $\cos\iota$ by taking the root-mean-square of a grid of values. Resonances with $n_\theta = 1$ ($2$; $3$) are coloured blue (gold; red). The $2$:$3$ resonance has the largest relative flux enhancement.}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics[width=0.46\textwidth]{res_flux_rms_p_e095}
\includegraphics[width=0.46\textwidth]{Fig_nu_rms_p}
\caption{\label{fig:res-flux-rms-p-vsnu}Relative flux enhancements of $p$ marginalised over $a_\ast$ and $\cos\iota$ by taking the root-mean-square. Resonances with $n_\theta = 1$ ($2$; $3$) are coloured blue (gold; red) and use circular (square; triangular) points.}
\end{figure}

>>>>

The absolute size of the resonance jump is often not particularly useful, especially when comparing different systems. Instead, we use the fractional enhancement relative to the adiabatic evolution,
\begin{equation}
\label{eq:res-jump-ratio}
\delta \mathcal{I}^a = \frac{\Delta \mathcal{I}^a\sub{jump}}{\dot{\mathcal{I}}^a\sub{ad}(t\sub{res})\tau\sub{res}}.
\end{equation}
Relative enhancements may be of the order of a few percent.

@@

\begin{figure}
\centering
%\includegraphics[width=0.46\textwidth]{res_flux_rms_p}
\includegraphics[width=0.46\textwidth]{Fig_e_rms_p}
\caption{\label{fig:res-flux-rms-p}Relative flux enhancements for the semilatus rectum $p$, as a function of $e$, marginalised over $a_\ast$ and $\cos\iota$ by taking the root-mean-square of a grid of values. Resonances with $n_\theta = 1$ ($2$; $3$) are coloured blue (gold; red). The $2$:$3$ resonance has the largest relative flux enhancement.}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics[width=0.46\textwidth]{res_flux_rms_p_e095}
\includegraphics[width=0.46\textwidth]{Fig_nu_rms_p}
\caption{\label{fig:res-flux-rms-p-vsnu}Relative flux enhancements for the semilatus rectum $p$ marginalised over $a_\ast$ and $\cos\iota$ by taking the root-mean-square. Resonances with $n_\theta = 1$ ($2$; $3$) are coloured blue (gold; red) and use circular (square; triangular) points.}
\end{figure}
